Exploratory Plots

### 2020-05-29 exploratory/2020/README.Rmd
Update plots with marine data

# Fitting datasets to a reference database vs _de novo_ clustering
```{r functions}
relevel_method <- function(df) {
  df %>%
    mutate(method = fct_relevel(method, c("open", "closed", "de_novo")))
}
plot_jitter <- function(df, y) {
  df %>% group_by(dataset, method) %>% 
      ggplot(aes(x=method, y={{ y }}, fill=dataset)) +
  geom_jitter()
}
```

@@

```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.txt'))
fractions %>% 
  ggplot(aes(dataset, fraction_mapped)) +
  geom_jitter()
```

>>>>

# Fitting datasets to a reference database vs _de novo_ clustering
```{r functions}
relevel_method <- function(df) {
  df %>%
    mutate(method = fct_relevel(method, c("open", "closed", "de_novo")))
}
plot_jitter <- function(df, y) {
  df %>% group_by(dataset, method) %>% 
      ggplot(aes(x=method, y={{ y }}, color=dataset)) +
  geom_jitter()
}
```

@@

```{r fit_db_input_size}

```

```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.txt'))
fractions %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=dataset)) +
  geom_jitter() +
  ylim(0, 1)
```
